\section{Introduction}
\label{sec:intro}
\noindent

As part of the development of software systems various artifacts ranging from quality models that capture the essential qualities relevant for a system, over the system's concrete requirements and design model, to the concrete implementation are developed. Within each artifact, different aspects of the system are interrelated, i.e., internal trace links. 
On the other side, traceability between the same system element and its representation in the different artifacts, i.e., external trace links, is typically maintained.
As part of these processes a significant amount of proactive effort is spent on creating and maintaining trace links, while it is unclear what are the trace links that later provide the most benefit.


Research questions:
\begin{enumerate}[label=\textbf{RQ\arabic*:}, ref=RQ\arabic*]
	\item What is the impact of internal and external trace links on issue prioritization?
	
	\item What is the impact of internal trace links within models, requirements, and code on traceability?
	
	\item What are the most important external trace links to maintain during the development of software systems?
	
\end{enumerate}

Methodology:
\begin{itemize}
	\item Empirical study based on artifacts
\end{itemize}

What do we need:
\begin{enumerate}
	\item More projects
	\subitem More realistic models, requirements etc
	\subitem Trace links
	\item Design of the experiments
\end{enumerate}

Case Studies:

\begin{itemize}
	\item Corona Warn App: Java, Component Diagram, Quality Model
	\item iTrust: Java, Requirements, TraceLinks
\end{itemize}

Potential Case Studies:
\begin{itemize}
	\item Eclipse Dataspace Connector @Sven
	\item Droneology \url{https://dronology.info/requirements/}
	\item KIT Dataset: \url{https://github.com/ardoco/benchmark/tree/main}
	\subitem BBB -> Large zoo of languages, only 11\% Java
	\subitem JabRef @Sven
	\subitem MediaStore
	\subitem Teammates \url{https://github.com/TEAMMATES/teammates}
	\subitem Teastore
	\item SAFA Dataset -> Security?
	\item Models mined by Daniel: Models, Code \url{https://doi.org/10.1007/s10270-025-01289-y} Probably not security critical examples
\end{itemize}